Plots and tables summarizing results of Poisson simulations

### 2019-11-12 analysis/motorcycle.Rmd
Simplifying some of the code in poisson.Rmd.

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Accident
data. Some additional functions are defined in
`functions.motorcycle.R`.

@@

>>>>

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Accident
data. Some additional functions are defined in file
`motorcycle.functions.R`.

@@

Finally, we compare the SMASH estimates (the orange
line) against the the mean estimates obtained by TI thresholding (dark
blue line) using RMAD.

```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
res.ti.rmad.mc <- tithresh.rmad.wrapper(x.ini.mc,y.ini.mc)

plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.ti.rmad.mc$x,res.ti.rmad.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
	 lwd = 2,col = "dodgerblue")
lines(res.mc$x,res.mc$mu.est - 2*sqrt(res.mc$var.est),
      lty = 5,lwd = 2,col = "dodgerblue")
legend(30, -100, c("TI-thresholding mean estimate", "SMASH mean estimate", "SMASH variance estimate"), col = c("darkblue", "darkorange", "dodgerblue"), bty = "n", lwd = 1, lty = c(1, 1, 5), pt.cex = 1, cex = 0.75)
```

### 2019-11-12 analysis/poisson.Rmd
Simplifying some of the code in poisson.Rmd.

The plots shown below for the "Bursts" simulations were included in
the manuscript.

@@

```{r table-row-and-col-names}
table.row.names <- c("SMASH","BMSM","Haar-Fisz")
table.col.names <- c("(1/100,3)","(1/8,8)","(1/128,128)")
```

@@

```{r load-pkgs, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(xtable)
```

Some of the test functions are defined in `signals.R`, so we load them
here:

```{r source-signals}
source("../code/signals.R")
```

@@

```{r spikes-table, results="asis"}
mise.s.table <- cbind(mise.s.1[methods],
                      mise.s.8[methods],
                      mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
kable(mise.s.table,format = "html",
  table.attr = paste("class=\"table\";","style=\"font-family: sans-serif;",
                     "width: auto; margin-left: auto; margin-right: auto\""))
```

@@

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots <- function (pdat1, pdat8, pdat128) {
  p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
}
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r angles-table, results="asis"}
mise.ang.table <- cbind(mise.ang.1[methods],
                        mise.ang.8[methods],
                        mise.ang.128[methods])
rownames(mise.ang.table) <- table.row.names
colnames(mise.ang.table) <- table.col.names
print(xtable(mise.ang.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

@@

```{r heavisine-table, results="asis"}
mise.hs.table <- cbind(mise.hs.1[methods],
                       mise.hs.8[methods],
                       mise.hs.128[methods])
rownames(mise.hs.table) <- table.row.names
colnames(mise.hs.table) <- table.col.names
print(xtable(mise.hs.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

@@

```{r bursts-table, results="asis"}
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
rownames(mise.bur.table) <- table.row.names
colnames(mise.bur.table) <- table.col.names
print(xtable(mise.bur.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

@@

```{r cb-table, results="asis"}
mise.cb.table <- cbind(mise.cb.1[methods],
                       mise.cb.8[methods],
                       mise.cb.128[methods])
rownames(mise.cb.table) <- table.row.names
colnames(mise.cb.table) <- table.col.names
print(xtable(mise.cb.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

@@

```{r bumps-table, results="asis"}
mise.b.table <- cbind(mise.b.1[methods],
                      mise.b.8[methods],
                      mise.b.128[methods])
rownames(mise.b.table) <- table.row.names
colnames(mise.b.table) <- table.col.names
print(xtable(mise.b.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

>>>>

The plots for the "Bursts" simulations shown below were also included
in the manuscript.

@@

```{r table-row-and-col-names}
```

@@

```{r load-pkgs, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
```

Some of the test functions are defined in `signals.R`, so we load them
here. Some additional functions are defined in file
`poisson.functions.R`.

```{r load-functions}
source("../code/poisson.functions.R")
source("../code/signals.R")
```

@@

```{r spikes-table, results="asis"}
mise.s.table <- cbind(mise.s.1[methods],
                      mise.s.8[methods],
                      mise.s.128[methods])
create.results.table(mise.s.table)
```

@@

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

```{r angles-table, results="asis"}
mise.ang.table <- cbind(mise.ang.1[methods],
                        mise.ang.8[methods],
                        mise.ang.128[methods])
create.results.table(mise.ang.table)
```

@@

```{r heavisine-table, results="asis"}
mise.hs.table <- cbind(mise.hs.1[methods],
                       mise.hs.8[methods],
                       mise.hs.128[methods])
create.results.table(mise.hs.table)
```

@@

```{r bursts-table, results="asis"}
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
create.results.table(mise.bur.table)
```

@@

```{r cb-table, results="asis"}
mise.cb.table <- cbind(mise.cb.1[methods],
                       mise.cb.8[methods],
                       mise.cb.128[methods])
create.results.table(mise.cb.table)
```

@@

```{r bumps-table, results="asis"}
mise.b.table <- cbind(mise.b.1[methods],
                      mise.b.8[methods],
                      mise.b.128[methods])
create.results.table(mise.b.table)
```
